### 2013-05-24 Publications/2013-TMI/04-methods.tex
Several minor fixes
  * Updated title (#82)
  * Very little changes on methods (#80)

Finally, we can turn the \gls{map} problem into a variational one
applying the following log-transform:
\begin{multline}
E(X \mid Y)= -\log \left[ p(X \mid Y) \, p(Y) \right] = \\
= -\log \left[ \underset{k}{\prod} \underset{\mathbf{x}\in \Omega_k}{\prod}
p_k( X(\mathbf{x}) \mid Y(\mathbf{x}) )^{d\mathbf{x}} \right] = \\
= \sum\limits_k \int_{\Omega_k} -\log \left[ p_k(X(\mathbf{x}) \mid Y(\mathbf{x} ) ) \right] \, d\mathbf{x},
\label{eq:energy_1}
\end{multline}
and introducing the posterior probability term \eqref{eq:bayes_mpdf}, we get:
\begin{multline}
E(X \mid Y) = \sum\limits_k \int_{\Omega_k} -\log \left[ \frac{1}{ \sqrt{(2\pi)^{C}\,\left|\boldsymbol{\Sigma}_{k}\right|}}\,{e^{\left(-\frac{1}{2}  \Delta^2_k (\mathbf{f}) \right)}} \right] \, d\mathbf{x} = \\
= \sum\limits_k \int_{\Omega_k} \left[ \frac{1}{2} \log{ \left( (2\pi)^{C}\,\left|\boldsymbol{\Sigma}_{k}\right| \right)} + \frac{1}{2}  \Delta^2_k (\mathbf{f}) \right] \,d\mathbf{x}.
\end{multline}
Finally, after removing scaling factors and independent constants,
we can express the functional in terms of $\lbrace\Theta_k,\Omega_k\rbrace$:
\begin{align}
E(\Theta_k,K) = \sum\limits_k \int_{\Omega_k} \left[ \log \left|\mathbf{\Sigma}_k\right| + \Delta^2_k (\mathbf{f}) \right] \,d\mathbf{x},
\label{eq:map_energy}
\end{align}
(\textbf{FIXME:} bad explanation) where we have a constant term scaled by
the total volume of the partition $\Omega_k$ and the determinant of the 
covariance matrix of the partition $\left|\boldsymbol{\Sigma}_{k}\right|$,
plus an energy term based on the squared \emph{Mahalanobis distance}.

@@

>>>>

Finally, we can turn the \gls{map} problem into a variational one
applying the following log-transform:
\begin{multline}
E(X \mid Y)= -\log \left[ p(X \mid Y) \, p(Y) \right] = \\
= -\log \left[ \underset{k}{\prod} \underset{\mathbf{x}\in \Omega_k}{\prod}
p_k( X(\mathbf{x}) \mid Y(\mathbf{x}) )^{d\mathbf{x}} \right] = \\
= \sum\limits_k \int_{\Omega_k} -\log \left[ p_k(X(\mathbf{x}) \mid Y(\mathbf{x} ) ) \right] \, d\mathbf{x},
\label{eq:energy_1}
\end{multline}
and introducing the posterior probability term \eqref{eq:bayes_mpdf}, 
we can express the functional in terms of $\lbrace\Theta_k,\Omega_k\rbrace$:
\begin{multline}
E(\Theta_k,\Omega_k) = \\
= \sum\limits_k \int_{\Omega_k} -\log \left[ \frac{1}{ \sqrt{(2\pi)^{C}\,\left|\boldsymbol{\Sigma}_{k}\right|}}\,{e^{\left(-\frac{1}{2}  \Delta^2_k (\mathbf{f}) \right)}} \right] \, d\mathbf{x} = \\
= \sum\limits_k \int_{\Omega_k} \left[ \frac{1}{2} \log{ \left( (2\pi)^{C}\,\left|\boldsymbol{\Sigma}_{k}\right| \right)} + \frac{1}{2}  \Delta^2_k (\mathbf{f}) \right] \,d\mathbf{x}.
\end{multline}
Finally, after removing scaling factors and independent constants,
we obtain:
\begin{align}
E(\Theta_k,\Omega_k) = \sum\limits_k \int_{\Omega_k} \left[ \log \left|\mathbf{\Sigma}_k\right| + \Delta^2_k (\mathbf{f}) \right] \,d\mathbf{x},
\label{eq:map_energy}
\end{align}
(\textbf{FIXME:} bad explanation) where we have a constant term scaled by
the total volume of the partition $\Omega_k$ and the determinant of the 
covariance matrix of the partition $\left|\boldsymbol{\Sigma}_{k}\right|$,
plus an energy term based on the squared \emph{Mahalanobis distance}.

@@

As long as we do not penalize the edge set $K$ length, $\nu = 0$ and
the result is dual to \eqref{eq:map_energy}:
\begin{equation}
E(\Theta_k,K) = \sum\limits_k \int_{\Omega_k} \left[ \log \left|\mathbf{\Sigma}_k\right| + \Delta^2_k (\mathbf{f}) \right] \,d\mathbf{x}.
\end{equation}

### 2013-05-24 Publications/2013-TMI/05-experiments.tex
Several minor fixes
  * Updated title (#82)
  * Very little changes on methods (#80)

\subsubsection{Real \gls{mri} datasets} %
%
We used image data from XX healthy volunteers with no history of neurological
conditions (ages XX$\pm$XX, X female) to illustrate the applicability of our 
approach. All the subjects were scanned in a 3T MR Scanner (Siemens Magnetom
TrioTim blah blah)
with an X-channel head coil. Subjects were scanned twice with the same protocol,
described hereafter. After being scanned the first time, each subject exited the
scan room for a short break and then reentered for an identical scan session.
To note, there was a full repositioning of the volunteer, coils, blankets and pads
before each scan and re-scan session.

The scan session protocol was as follows:
\begin{enumerate}
\item Triplanar survey (Localizer).
\item Field Mapping: field mapping using GRE sequence was performed before \gls{dwi}
acquisition for susceptibility correction purposes.
\item DTI: \gls{dwi} were acquired with axial in-plane 
isotropic resolution $2mm$, slice thickness $2mm$, $XXX \times XXX \times XXX$ 
image matrix, TR= XXXX ms, TE = XX ms, NEX = X, BW = XXXX Hz/pixel, GRAPPA
acceleration factor 2. The series included images acquired with diffusion
weighting along 30 non-collinear directions ( $b$=700sm$^{-2}$ ) sampled
twice for averaging, and 5 interleaved images acquired without diffusion 
weighting ( $b=0$ ).
\item Field Mapping (same as before DTI)
\item Structural T1: An MPRAGE T1-weighted acquisition, sagittal
GRE sequence, in-plane isotropic resolution 1.0 mm, slice thickness 1.2mm
$XXX \times XXX \times XXX$ image matrix, TR=2300 ms, TE=2.98 ms, FA= 9, NEX=X, BW= 240 Hz/pixel.
\item Structural T2: A T2-weighted acquisition, oblique axial
TSE sequence, in-plane isotropic resolution 1.0 mm, slice thickness 1.2mm
$XXX \times XXX \times XXX$ image matrix, TR=3200 ms, TE= 408 ms, NEX=X, BW= 751 Hz/pixel.
\end{enumerate}

>>>>

\subsubsection{Real \gls{mri} datasets} %
%
We used image data from XX healthy volunteers with no history of neurological
conditions (ages XX$\pm$XX, X female) to illustrate the applicability of our 
approach. All the subjects were scanned in a 3T MR Scanner (Siemens Magnetom
TrioTim, Siemens, Erlangen, Germany) with a standard 12-channel head coil. 
(\textbf{FIXME:} check coil number of channels!!)
Subjects were scanned twice with the same protocol,
described hereafter. After being scanned the first time, each subject exited the
scan room for a short break and then reentered for an identical scan session.
To note, there was a full repositioning of the volunteer, coils, blankets and pads
before each scan and re-scan session. The scan session protocol was as follows:
\begin{enumerate}
\item Triplanar survey (Localizer).
\item Field Mapping: field mapping using GRE sequence was performed before \gls{dwi}
acquisition for susceptibility correction purposes.
\item DTI: \gls{dwi} were acquired with axial in-plane 
isotropic resolution $2mm$, slice thickness $2mm$, $XXX \times XXX \times XXX$ 
image matrix, TR= XXXX ms, TE = XX ms, NEX = X, BW = XXXX Hz/pixel, GRAPPA
acceleration factor 2. The series included images acquired with diffusion
weighting along 30 non-collinear directions ( $b$=700sm$^{-2}$ ) sampled
twice for averaging, and 5 interleaved images acquired without diffusion 
weighting ( $b=0$ ).
\item Field Mapping (same as before DTI)
\item Structural T1: An MPRAGE T1-weighted acquisition, sagittal
GRE sequence, in-plane isotropic resolution 1.0 mm, slice thickness 1.2mm
$XXX \times XXX \times XXX$ image matrix, TR=2300 ms, TE=2.98 ms, FA= 9, NEX=X, BW= 240 Hz/pixel.
\item Structural T2: A T2-weighted acquisition, oblique axial
TSE sequence, in-plane isotropic resolution 1.0 mm, slice thickness 1.2mm
$XXX \times XXX \times XXX$ image matrix, TR=3200 ms, TE= 408 ms, NEX=X, BW= 751 Hz/pixel.
\end{enumerate}
